Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-10 draft.tex
add link to repository
improve discussion and conclusion

	such feature combinations.

@@

		pitch fluctuations having not influence on the outcome whatsoever. Unlike the previous

@@

		between these features and the realness of audio samples in the dataset. These features

@@

		the difference was still minimal. In spite of this, we believe that it is still worth
		investigating if other kinds of perceptible features will have more of an influence on the
		overall classification or if there are other imperceptible features that could be used in
		the place of MFCCs that may provide a better balance between classification correctness
		and a proportional influence on the end result.

@@

	and shimmer.

@@

	We believe that this is a method that offers a large potential, but is not useful for the
	generation of understandable explanations in its current state. We suggest, however, that this
	method could be changed and improved in the future with other features or other changes to
	base parameters that could potentially produce more useful explanations while either holding
	the accuracy high like it is now or even improving it further.

>>>>

	such feature combinations. For the purpose of reproducibility, the source code for these
	experiments is open in the following repository:
	\url{https://github.com/jacoblarock/fake_voices_xai}

@@

		pitch fluctuations having no influence on the outcome whatsoever. Unlike the previous

@@

		between these features and the authenticity of audio samples in the dataset. These features

@@

		the difference was still minimal. In the case of perceptible features with a positive
		trust score, the potential remains for their potential use in understandable explanations
		as, even though the classification needle of the model was not moved largely by these
		features, they still demonstrate a certain reliability. In spite of this, we believe that
		it is still worth investigating if other kinds of perceptible features will have more of
		an influence on the overall classification or if there are other imperceptible features
		that could be used in the place of MFCCs that may provide a better balance between
		classification correctness and a proportional influence on the end result, so that the
		usefulness of the explanations can be even stronger than the method using the above
		feature combinations, and we believe that this kind of model architecture paired with LIME
		and evaluated with the presented metrics has the potential to be a backbone for future
		research.

@@

	and shimmer, which offer potential to be used in explanations.

@@

	We believe that this is a method that offers a large potential, but is not yet in a fully
	mature state. We suggest, however, that this method could be changed and improved in the
	future with other features or other changes to base parameters that could potentially produce
	more useful explanations while either holding the accuracy high like it is now or even
	improving it further.
